Smart quotes, em dashes, and en dashes

### 2024-06-20 text/20/ihme-model.Rmd
Update 2020 files

---
title: "Criticisms of the IHME COVID-19 model"
author: "Steve Simon"
source: "New"
categories:
- Blog post
tags:
- Epidemiology
output: html_document
---

>>>>

---
title: "Criticisms of the IHME COVID-19 model"
author: "Steve Simon"
source: new
date: 2020-04-23
categories:
- Blog post
tags:
- Epidemiology
output: html_document
page_update: complete
---

### 2024-06-20 text/20/map-projections.Rmd
Update 2020 files

---
title: "Blog post: Different map projections"
author: "Steve Simon"
source: "New"
date: "2020-03-15"
categories: Blog post
tags: Graphical display
output: html_document
---

>>>>

---
title: "Different map projections"
author: "Steve Simon"
source: new
date: "2020-03-15"
categories:
- Blog post
tags:
- Graphical display
output: html_document
page_update: complete
---
install.packages("rnaturalearthhires", repos="http://packages.ropensci.org", type="source")

### 2024-06-20 text/20/poor-color-choice.Rmd
Update 2020 files

---
title: "An example of a poor color choice"
author: "Steve Simon"
source: new
date: "2020-03-11"
categories:
- Blog post
tags:
- Graphical display
output: html_document
---

>>>>

---
title: "An example of a poor color choice"
author: "Steve Simon"
source: new
date: "2020-03-11"
categories:
- Blog post
tags:
- Graphical display
output: html_document
page_update: complete
---

### 2024-06-20 text/20/reading-text-files.Rmd
Update 2020 files

---
title: "Reading text files"
author: "Steve Simon"
source: new
date: "2020-04-30"
categories:
- Blog post
tags:
- Data management
output: html_document
---

>>>>

---
title: "Reading text files"
author: "Steve Simon"
source: new
date: "2020-04-30"
categories:
- Blog post
tags:
- Data management
output: html_document
page_update: complete
---

### 2024-06-20 text/20/rmarkdown-papers.Rmd
Update 2020 files

---
title: "How I use R Markdown to write research papers"
source: new
date: "2020-11-21"
categories:
- Blog post
tags:
- Writing research papers
output: html_document
---

>>>>

---
title: "How I use R Markdown to write research papers"
source: new
date: "2020-11-21"
categories:
- Blog post
tags:
- Writing research papers
output: html_document
page_update: complete
---

### 2024-06-20 text/20/smart-quotes.Rmd
Update 2020 files

---
title: "Smart quotes, em dashes, and en dashes"
author: "Steve Simon"
source: new
date: "2020-03-02"
categories:
- Blog post
tags:
- Data management
output: html_document
---

>>>>

---
title: "Smart quotes, em dashes, and en dashes"
author: "Steve Simon"
source: new
date: "2020-03-02"
categories:
- Blog post
tags:
- Data management
output: html_document
page_update: complete
---
